Perturbed Gait Data

### 2014-10-20 paper.tex

>>>>

\section{Conclusion}

We have presented the details of what we believe to be a rich dataset of motion
and ground reaction loads humans exhibit when recovering from minor
longitudinal perturbations. The data provides a large sample of gait cycles
from both unperturbed and perturbed walking at three different nominal speeds.
The raw data is provided for reuse with sufficient detail with regards to meta
data and technical details. In addition to the data, we provide software that
can process the data for cleaning purposes and to produce typical saggital
plane gait variables of interest. Among other uses, we believe the dataset is
ideally suited for control identification purposes. Many researchers are
working on mathematical models for control in gait and this dataset provides
both a way to validate these models and data that can be used to generate
models.
